### 2019-01-04 manuscript/manuscript.rmd
added summary figure for new analyses

```{r support}

analyses %>% 
	ggplot( aes(x=model_summary, y=clade, col=result) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic()
```

A total of `r nrow(analyses)` analyses were transcribed from the literature.

@@

```{r}

>>>>

```{r support_published_analyses}

analyses_published %>% 
	ggplot( aes(x=model_summary, y=clade, col=result) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic()

A total of `r nrow(analyses_published)` analyses were transcribed from the literature.

@@

```{r support_new_analyses}

analyses_new %>% 
	ggplot( aes(x=model_summary, y=clade, col=result, shape=modelfinder) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic()
```
